RadLib: a radiative property model library for CFD

### 2021-10-11 manuscript/manuscript.tex
DOL timing: might also add a norad case later

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models. Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs. Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared.
RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}

@@

Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. The calculation depends on a user-specified radiation path length variable with a default value of 0.1 m, which is used in the FM Burner validation case. Further details are provided in the FDS user guide \cite{FDS}. Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions. The models produce centerline temperature differences of about 80 K (7\%) between the RCSLW and the WSGG at z=2.5D, and 90 K (12\%) at z=3.5D. The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 1.3 kW/m (11\%).
%
\begin{figure}
\begin{center}
\begin{tabular}{c c}
(a) & (b) \\
\includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
\includegraphics[width=2.5 in]{fig_fds_rad_mean.pdf}
\end{tabular}
\caption{Radial profiles of mean temperature at two heights (a) and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
\label{f:fds}
\end{center}
\end{figure}
%

@@

>>>>

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}

@@

Figure~\ref{f:fds} shows results of the simulation with comparison to experimental data. Three radiation models were included: the FDS default model, and the RCSLW and WSGG models from RadLib (both using four gray gases and one clear gas).
The FDS default model uses a single gray gas with a composition and temperature dependent absorption coefficient computed from RADCAL. The calculation depends on a user-specified radiation path length variable with a default value of 0.1 m, which is used in the FM Burner validation case. Further details are provided in the FDS user guide \cite{FDS}. Figure~\ref{f:fds}a shows radial profiles of mean temperature at two vertical positions. The models produce maximum radial temperature differences at 1.5R of about 70 K (6\%) between the RCSLW and the WSGG at z=2.5D, and 50 K (6\%) at z=3.5D. 
%The differences are lower at lower points in the flame since the effect of radiation on temperature is cumulative. 
Figure~\ref{f:fds}b plots height versus radiative emission per unit length along the centerline with the spread in radiative emission around the peak values being 0.94 kW/m (8\%).
%
\begin{figure}
\begin{center}
\begin{tabular}{c c}
(a) & (b) \\
\includegraphics[width=2.5 in]{fig_fds_T_mean.pdf} &
\includegraphics[width=2.5 in]{fig_fds_rad_mean.pdf}
\end{tabular}
\caption{Radial profiles of mean temperature at two heights (a) and height versus radiative emission (b) for FDS simulations of the FM Burner validation case comparing three models to experimental data.}
\label{f:fds}
\end{center}
\end{figure}
%

@@

The computational cost of the FDS simulations, relative to the default model are 1, 1.68, and 1.71 for the default, WSGG, and RCSLW model, respectively. This indicates that the cost is dominated by the radiative solver and not the computation of the radiative properties.
